{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-22 thesis/education.tex
small revisions to bugfinding

Firstly, I sought to prove Landslide does as advertised:
finds concurrency bugs of severity, subtlety, and difficulty
consistent with the lessons an advanced operating systems class should hope to teach its students,
and provides diagnostic output that helps the student to understand and solve them.
% without necessarily spoiling the answer to the puzzle ... not scientifically evaluatable,
% but at least the trace format is de0u-approved.

@@

At U. Chicago,
course staff ran Landslide on student submissions behind-the-scenes
after each project deadline had passed,
and returned its preemption traces to any study volunteers.
I collaborated with the course staff
to confirm whether each trace represented a real bug and not a false positive
before distributing them to the students.
We decided on this procedure to optimize for most benefit to the students rather than for scientific rigor,
due to the small sample size (4 volunteering student groups among 21 submitted projects).

@@

% XXX: did I actually fix this in the annotation scripts, or did I just hackhackhack to suppress it?
% my email to kevin just says, "I suppressed the false positive bug from wait-simple in GROUPNAME and got a real bug next".
Finally, one false positive was found while testing {\tt wait-simple}.
Landslide mistakenly reported that {\tt free()} had reentered {\tt malloc()},
which would be a potential heap corruption bug,
due to a technical discrepancy between when Pebbles and Pintos kernels take and release their heap allocation lock
with regard to the rest of the {\tt malloc()} API.
After discarding the bug report and suppressing this false positive,
Landslide moved on to find the true deterministic use-after-free described above.

>>>>

Firstly, I sought to prove Landslide does as advertised:
finds concurrency bugs of severity, subtlety, and difficulty
consistent with the lessons an advanced operating systems class should hope to teach its students,
and provides diagnostic output that helps students understand and solve them.
% without necessarily spoiling the answer to the puzzle ... not scientifically evaluatable,
% but at least the trace format is de0u-approved.

@@

At U. Chicago,
course staff ran Landslide on student submissions behind-the-scenes
after each project deadline had passed,
and returned its preemption traces to the study volunteers.
I collaborated with the course staff
to confirm whether each trace represented a real bug and not a false positive
before distributing them to the students.
On account of the small sample size (4 volunteering groups),
we decided on this approach,
rather than to study how students would cope with false positives themselves,
to optimize for student happiness over scientific rigor.

@@

% XXX: did I actually fix this in the annotation scripts, or did I just hackhackhack to suppress it?
% my email to kevin just says, "I suppressed the false positive bug from wait-simple in GROUPNAME and got a real bug next".
Finally, one false positive was found while testing {\tt wait-simple}.
Landslide mistakenly reported that {\tt free()} had reentered {\tt malloc()}
(normally a heap corruption bug)
due to a technical discrepancy between when Pebbles and Pintos kernels take and release their heap allocation lock
with regard to the rest of the {\tt malloc()} API.
After discarding the bug report and suppressing this false positive,
Landslide moved on to find the true deterministic use-after-free described above.
